\chapter{Culture test}

This is inspired by Mark Rosenfelder's American culture test.

\section*{You know you're Tvellas if...}

\begin{itemize}
    \item You may or may not believe in the many gods. If you do, you believe that every people has
        its own gods, and they should be respected. People who insist that there is only one god are
        weird. Exactly which gods you believe in, even you may not be sure of.
    \item Your society has a lopsided sex ratio (almost twice as many women as there are men).
    \item If you're a (straight) man, you relish in the number of options you have for dating, but
        you may also be suspicious of foreigners who visit just to date the many single women in
        your country. Or if you're more conservative, you may fear that those foreigners are human
        traffickers trying to sell them to other countries as brides.
    \item If you're a woman, you feel like your society is safer and less militiant than any other.
\end{itemize}

\section*{Everyone knows that...}

\begin{itemize}
    \item If a man has sex with a man, he is gay, or bisexual. The older, more conservative
        generation might not understand why a man would fall in love with another man
    \item If a woman has sex with a woman, that's just normal.
    \item A man usually gets one wife at a time, but two isn't unusual. Group marriages are somewhat
        common -- usually these consist of two men and 2-4 women -- but not the norm, and they're
        not legally recognized. Many people are monogamous, but you wouldn't be looked down upon for
    \item Aside from men and women, there is a third gender, the [TERM MISSING].
\end{itemize}

\section*{}
